Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an empirical study of the Moran process for the iterated Prisoner's dilemma using reinforcement learning

### 2017-07-10 main.tex
Include pointer at Dojo.

All of the training code is available in the
Axelrod repository with documentation to train new strategies easily. Training
% TODO Include link etc
typically takes less than 100 generations and can be completed within several
hours on commodity hardware.

>>>>

All of the training code is archived at \cite{marc_harper_2017_824264}. This
software is (similarly to the Axelrod library) available on github
\url{https://github.com/Axelrod-Python/axelrod-dojo} with documentation to
train new strategies easily. Training
typically takes less than 100 generations and can be completed within several
hours on commodity hardware.
